---
title: "Credibility: Survey 2 Analysis"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(grid)
library(gridExtra)
library(stargazer)
library(lme4)


theme_credibility <- theme_minimal() + 
  theme(plot.title = element_text(size = 14, face = "bold"),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 14),
        legend.position = "none")

theme_set(theme_credibility)

boxplot_width = 0.7
jitter_width = 0.28
jitter_height = 0.25
jitter_alpha = 0.2

prop_text_size = 2.8
```

```{r}

# Update these dropbox links to point to your own path
# survey2_results_path <- "~/Dropbox/credibility/Data/New/results_bothRoundsCombined_validationFailsRemoved_art8redosadded.csv"
# tweets_guide_path <- "~/Dropbox/credibility/Data/New/codebook/tweetsGuide.csv"
survey2_results_path <- "../data/survey2/results_bothRoundsCombined_validationFailsRemoved_art8redosadded.csv"
tweets_guide_path <- "../data/survey2/codebook/tweetsGuide.csv"

# Load the data
survey2_results <- readr::read_csv(survey2_results_path, col_types = readr::cols())
tweetsGuide <- readr::read_csv(tweets_guide_path, col_types = readr::cols())


survey2_cleaned <- survey2_results %>%
  tidyr::gather(input, link, 29:42) %>%
  group_by(HITId, input) %>%
  mutate(
    input.num = as.numeric(strsplit(input, ".", fixed = T)[[1]][2]),
    Answer.Credibility = switch(input.num, 
                   Answer.Q1Credibility, 
                   Answer.Q2Credibility, 
                   Answer.Q3Credibility, 
                   Answer.Q4Credibility, 
                   Answer.Q5Credibility, 
                   Answer.Q6Credibility,
                   Answer.Q7Credibility,
                   Answer.Q8Credibility,
                   Answer.Q9Credibility,
                   Answer.Q10Credibility,
                   Answer.Q11Credibility,
                   Answer.Q12Credibility,
                   Answer.Q13Credibility,
                   Answer.Q14Credibility)
  ) %>%
  ungroup() %>%
  select(HITId, input, link, Answer.Age, Answer.Education, Answer.Gender, Answer.US, Answer.Credibility) %>%
  left_join(tweetsGuide, by = c("link" = "http")) %>%
  mutate(reception = as.factor(reception),
         topic = as.factor(topic),
         Answer.Age = Answer.Age / 10,
         Answer.Gender = as.factor(Answer.Gender),
         Answer.Education = as.factor(Answer.Education),
         Answer.US = as.factor(Answer.US),
         Title = factor(Title, levels = c("Title", "Neutral paraphrase", "Positive paraphrase")),
         Answer.Education = ifelse(Answer.Education %in% c("Bachelor", "Master", "Doct", "Professional"), "University+", "Associate-"),
         visual = factor(visual, levels = c("no visual", "chart from paper", "screenshot of abstract"))
         )
```

```{r}
summary(survey2_cleaned %>%
          group_by(HITId) %>%
          slice(1) %>%
          ungroup() %>%
          select(Answer.Age, Answer.Education, Answer.Gender, Answer.US) %>%
          mutate(
            Answer.Age = Answer.Age * 10,
            Answer.Education = as.factor(Answer.Education)
          )
        )

```

First we construct the visualization of the regression coefficients
```{r}
### original linear model ###

# model <- lm(Answer.Credibility ~
#               ownership + visual + reception + Title + # feature variables
#               topic + Answer.Gender + Answer.Education + Answer.US + Answer.Age, #control variables
#             survey2_cleaned)

#############################

### new mixed effect model ### 

model <- lmer(Answer.Credibility ~
              ownership + visual + reception + Title + # feature variables
              topic + Answer.Gender + Answer.Education + Answer.US + Answer.Age + #control variables
              (1|HITId),

            survey2_cleaned)

##############################
```


```{r}
broom::tidy(model, conf.int = T)

name_mapping = c(
  "ownershipownership" = "Author claims ownership",
  "visualchart from paper" = "Visual: Chart from paper",
  "visualscreenshot of abstract" = "Visual: Screenshot of abstract",
  "reception2" = "Reception: Medium",
  "reception3" = "Reception: High",
  "TitlePositive paraphrase" = "Title: Positive Paraphrase",
  "TitleNeutral paraphrase" = "Title: Neutral Paraphrase",
  "topic2" = "Topic 2",
  "topic3" = "Topic 3",
  "topic4" = "Topic 4",
  "topic5" = "Topic 5",
  "topic6" = "Topic 6",
  "topic7" = "Topic 7",
  "topic8" = "Topic 8", 
  "topic9" = "Topic 9",
  "topic10" = "Topic 10",
  "topic11" = "Topic 11",
  "topic12" = "Topic 12",
  "topic13" = "Topic 13",
  "topic14" = "Topic 14",
  "Answer.GenderMale" = "Gender: Male",
  "Answer.EducationUniversity+" = "Education: University+",
  "Answer.USYes" = "Location: In the U.S.",
  "Answer.Age" = "Age"
)

# Convert to a tidy model
model.tidy <- broom::tidy(model, conf.int = T)

# Now construct the regression plot from the tidy model
survey2_reg <- model.tidy %>%
  mutate(type = ifelse(grepl("topic",term), "Control", ifelse(grepl("Answer",term), "Control", "Feature")),
         term = as.factor(term),
         term = reorder(term, estimate),
         term = plyr::revalue(term, name_mapping)
        ) %>%
  filter(term != "(Intercept)"& term != "sd_(Intercept).HITId" & term != "sd_Observation.Residual") %>%
  ggplot(aes(x = term, y = estimate, color = type, shape = type)) +
    geom_point(size = 2.5) +
    # Only plot the values for feature variables
    geom_text(aes(label = ifelse(type == "Feature", round(estimate, 2), "")), nudge_x = 0.4, size = 3.5) +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.4) +
    geom_hline(yintercept = 0, color = "darkgrey") +
    coord_flip() + # flip horizontally
    scale_shape_manual(values = c(1, 19)) +
    scale_color_manual(values = c("darkgrey", "black")) + 
    guides(color = F) +
    labs(title = "A. Model coefficients",
         y = "Estimate") +
    theme(
      axis.title.y = element_blank()
    ) 

survey2_reg
```

check residual plots 
```{r}

model.resid = resid(model)
model.fitted = fitted(model)
model_test = data.frame(model.resid, model.fitted)

ggplot(model_test, aes(x=model.fitted, y=model.resid)) + geom_point() + geom_smooth(method = "loess")

```

```{r}

# ranef(model)

reaction_subject <- fixef(model) + ranef(model)$HITId
reaction_subject$Subject<-rownames(reaction_subject)
names(reaction_subject)[1]<-"Intercept"
reaction_subject <- reaction_subject[,c(2,1)]
#plot
ggplot(reaction_subject,aes(x=Subject,y=Intercept))+geom_point() + geom_smooth(method="lm")

```
The regression table should also be provided. Here we will create a regression table using the stargazer package. 

To insert this into microsoft word, open the "survey2_table.html" file in a web brower and copy it from there into the document
```{r}
survey2_table <- stargazer(
  model, 
  ci = TRUE,
  covariate.labels = name_mapping,
  type = "html")

write(survey2_table, "survey2_reg_table.html")
```

Similarly, we will also output the ANOVA table of the model using stargazer and the same procedure to bring into a microwoft word document. 
```{r}
anova_mapping <- c(
  "ownership" =  "Claim of ownership",
  "reception" = "Reception",
  "visual" = "Presence of visual",
  "Title" = "Title phrasing",
  "topic" = "Topic of paper",
  "Answer.Gender" = "Gender of respondant",
  "Answer.Education" = "Education of respondant",
  "Answer.US" = "Respondant from U.S.",
  "Answer.Age" = "Respondant age"
)

survey2_anova <- anova(model)
rownames(survey2_anova) <- plyr::revalue(rownames(survey2_anova), anova_mapping)

survey2_anova_table <- stargazer(survey2_anova, summary = FALSE, type = "html")

write(survey2_anova_table, "survey2_anova_table.html")
```

Next we will create bar charts that will be displayed alongside the regression visualization. There will be a total of four charts, one for each of the feature variables. 
```{r}
survey2_visual_labels <- survey2_cleaned %>%
  mutate(
        visual = as.factor(visual),
        visual = plyr::revalue(visual, 
                           c("no visual" = "No Visual", 
                             "chart from paper" = "Chart from\nPaper", 
                             "screenshot of abstract" = "Screenshot\nof Abstract"))
  ) %>%
  group_by(visual) %>%
  mutate(total = n()) %>%
  group_by(visual, Answer.Credibility) %>%
  summarize(
    prop = n() / total[1]
  )

survey2_visual_means <- survey2_cleaned %>%
  mutate(
        visual = as.factor(visual),
        visual = plyr::revalue(visual, 
                           c("no visual" = "No Visual", 
                             "chart from paper" = "Chart from\nPaper", 
                             "screenshot of abstract" = "Screenshot\nof Abstract"))
  ) %>%
  group_by(visual) %>%
  summarize(mu = mean(Answer.Credibility, na.rm = T))


survey2_visual <- survey2_cleaned %>%
  mutate(
    visual = as.factor(visual),
    visual = plyr::revalue(visual, 
                           c("no visual" = "No Visual", 
                             "chart from paper" = "Chart from\nPaper", 
                             "screenshot of abstract" = "Screenshot\nof Abstract"))
  ) %>%
  ggplot(aes(x = visual, y = Answer.Credibility, fill = visual)) +
    geom_boxplot(color = "black", width = boxplot_width, notch = T) +
    geom_jitter(width = jitter_width, height = jitter_height, alpha = jitter_alpha, shape = 21) +
    geom_segment(data = survey2_visual_means, aes(x = as.numeric(visual) - 0.5, xend = as.numeric(visual) + 0.5, y = mu, yend = mu), color = "#e74c3c", size = 2) +
    geom_label(data = survey2_visual_labels, aes(label = paste0(round(prop * 100, 1), "%")), alpha = 0.85, size = prop_text_size) +
    coord_flip(ylim = c(0.7, 7.3), expand = TRUE) +
    scale_y_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7)) +  
    labs(y = "Avg. Credibility",
         title = "B. Presence of visual") +
    scale_fill_brewer(palette = "Greens") +
    guides(fill = F) +
    theme(axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          panel.grid.major.y = element_blank(),
          panel.grid.minor.x = element_blank()
          ) 

survey2_visual
```

```{r}
survey2_ownership_labels <- survey2_cleaned %>%
  mutate(
        ownership = factor(ownership),
        ownership = plyr::revalue(ownership, 
                                  c("no ownership" = "No Ownership\nClaimed", 
                                    "ownership" = "Author Claims\nOwnership"))
  ) %>%
  group_by(ownership) %>%
  mutate(total = n()) %>%
  group_by(ownership, Answer.Credibility) %>%
  summarize(
    prop = n() / total[1]
  )

survey2_ownership_means <- survey2_cleaned %>%
  mutate(
        ownership = factor(ownership),
        ownership = plyr::revalue(ownership, 
                                  c("no ownership" = "No Ownership\nClaimed", 
                                    "ownership" = "Author Claims\nOwnership"))
  ) %>%
  group_by(ownership) %>%
  summarize(mu = mean(Answer.Credibility, na.rm = T))

survey2_ownership <- survey2_cleaned %>%
  #rowwise() %>%
  mutate(
    ownership = factor(ownership),
    ownership = plyr::revalue(ownership, 
                              c("no ownership" = "No Ownership\nClaimed", 
                                "ownership" = "Author Claims\nOwnership"))
  ) %>%
  ggplot(aes(x = ownership, y = Answer.Credibility, fill = ownership)) +
    geom_boxplot(color = "black", width = boxplot_width, notch = T) +
    geom_jitter(width = jitter_width, height = jitter_height, alpha = jitter_alpha, shape = 21) +
    geom_segment(data = survey2_ownership_means, aes(x = as.numeric(ownership) - 0.5, xend = as.numeric(ownership) + 0.5, y = mu, yend = mu), color = "#e74c3c", size = 2) +
    geom_label(data = survey2_ownership_labels, aes(label = paste0(round(prop * 100, 1), "%")), alpha = 0.85, size = prop_text_size) +
    coord_flip(ylim = c(0.7, 7.3), expand = TRUE) +
    scale_y_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7)) +  
    labs(y = "Avg. Credibility",
         title = "D. Claim of ownership") +
    scale_fill_brewer(palette = "Blues") +
    guides(fill = F) +
    theme(axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          panel.grid.major.y = element_blank(),
          panel.grid.minor.x = element_blank()
          ) 

survey2_ownership
```

```{r}
survey2_title_labels <- survey2_cleaned %>%
  mutate(
        Title = factor(Title, 
                       levels = c("Title", "Neutral paraphrase", "Positive paraphrase"),
                       labels = c("Not\nParaphrased", "Neutral\nParaphrase", "Positive\nParaphrase"))
  ) %>%
  group_by(Title) %>%
  mutate(total = n()) %>%
  group_by(Title, Answer.Credibility) %>%
  summarize(
    prop = n() / total[1]
  )

survey2_title_means <- survey2_cleaned %>%
  mutate(
        Title = factor(Title, 
                       levels = c("Title", "Neutral paraphrase", "Positive paraphrase"),
                       labels = c("Not\nParaphrased", "Neutral\nParaphrase", "Positive\nParaphrase"))
  ) %>%
  group_by(Title) %>%
  summarize(mu = mean(Answer.Credibility, na.rm = T))

survey2_title <- survey2_cleaned %>%
  mutate(
    Title = factor(Title, 
                   levels = c("Title", "Neutral paraphrase", "Positive paraphrase"),
                   labels = c("Not\nParaphrased", "Neutral\nParaphrase", "Positive\nParaphrase"))
  ) %>%
  ggplot(aes(x = Title, y = Answer.Credibility, fill = Title)) +
    geom_boxplot(color = "black", width = boxplot_width, notch = T) +
    geom_jitter(width = jitter_width, height = jitter_height, alpha = jitter_alpha, shape = 21) +
    geom_segment(data = survey2_title_means, aes(x = as.numeric(Title) - 0.5, xend = as.numeric(Title) + 0.5, y = mu, yend = mu), color = "#e74c3c", size = 2) +
    geom_label(data = survey2_title_labels, aes(label = paste0(round(prop * 100, 1), "%")), alpha = 0.85, size = prop_text_size) +
    coord_flip(ylim = c(0.7, 7.3), expand = TRUE) +
    scale_y_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7)) +  
    labs(y = "Avg. Credibility",
         title = "C. Title phrasing") +
    scale_fill_brewer(palette = "Purples") +
    guides(fill = F) +
    theme(axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          panel.grid.major.y = element_blank(),
          panel.grid.minor.x = element_blank()
          ) 
    
survey2_title
```


```{r}
survey2_reception_labels <- survey2_cleaned %>%
  mutate(
        reception = factor(reception, labels = c("Low", "Moderate", "High"))
  ) %>%
  group_by(reception) %>%
  mutate(total = n()) %>%
  group_by(reception, Answer.Credibility) %>%
  summarize(
    prop = n() / total[1]
  )

survey2_reception_means <- survey2_cleaned %>%
 mutate(
        reception = factor(reception, labels = c("Low", "Moderate", "High"))
  ) %>%
  group_by(reception) %>%
  summarize(mu = mean(Answer.Credibility, na.rm = T))


survey2_reception <- survey2_cleaned %>%
  mutate(
    reception = factor(reception, labels = c("Low", "Moderate", "High"))
  ) %>%
  ggplot(aes(x = reception, y = Answer.Credibility, fill = reception)) +
    geom_boxplot(color = "black", width = boxplot_width, notch = T) +
    geom_jitter(width = jitter_width, height = jitter_height, alpha = jitter_alpha, shape = 21) +
    geom_segment(data = survey2_reception_means, aes(x = as.numeric(reception) - 0.5, xend = as.numeric(reception) + 0.5, y = mu, yend = mu), color = "#e74c3c", size = 2) +
    geom_label(data = survey2_reception_labels, aes(label = paste0(round(prop * 100, 1), "%")), alpha = 0.85, size = prop_text_size) +
    coord_flip(ylim = c(0.7, 7.3), expand = TRUE) +
    scale_y_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7)) +  
    labs(y = "Avg. credibility",
         title = "E. Reception") +
    scale_fill_brewer(palette = "Oranges") +
    guides(fill = F) +
    theme(axis.title.y = element_blank(),
          panel.grid.major.y = element_blank(),
          panel.grid.minor.x = element_blank()
          ) 
    
survey2_reception
```


Now that each of the graphs have been created, we can combine them into a single figure
```{r}
plots <- list(survey2_visual, survey2_title, survey2_ownership, survey2_reception)
grobs <- list()
widths <- list()
heights <- list()

for (i in 1:length(plots)){
    grobs[[i]] <- ggplotGrob(plots[[i]])
    widths[[i]] <- grobs[[i]]$widths[2:5]
    heights[[i]] <- grobs[[i]]$heights[2:5]
}

maxwidth <- do.call(grid::unit.pmax, widths)
maxheight <- do.call(grid::unit.pmax, heights)

for (i in 1:length(grobs)){
     grobs[[i]]$widths[2:5] <- as.list(maxwidth)
     grobs[[i]]$heights[2:5] <- as.list(maxheight)
}

g1 <- do.call("grid.arrange", c(grobs, ncol = 1))

g <- grid.arrange(survey2_reg, g1, ncol = 2)
# ggsave("~/Desktop/survey2_credibility_fig.png", g, width = 9, height = 9)
ggsave("survey2_credibility_fig.png", g, width = 9, height = 9)
ggsave("survey2_credibility_fig.pdf", g, width = 9, height = 9)
```

```{r}
survey2_topic_labels <- survey2_cleaned %>%
  group_by(topic) %>%
  mutate(total = n()) %>%
  group_by(topic, Answer.Credibility) %>%
  summarize(
    prop = n() / total[1]
  )

survey2_topic_means <- survey2_cleaned %>%
  group_by(topic) %>%
  summarize(mu = mean(Answer.Credibility, na.rm = T))


survey2_topic <- survey2_cleaned %>%
  ggplot(aes(x = topic, y = Answer.Credibility)) +
    geom_boxplot(color = "black", width = boxplot_width, notch = T) +
    geom_jitter(width = jitter_width, height = jitter_height, alpha = jitter_alpha, shape = 21) +
    geom_segment(data = survey2_topic_means, aes(x = as.numeric(topic) - 0.5, xend = as.numeric(topic) + 0.5, y = mu, yend = mu), color = "#e74c3c", size = 2) +
    geom_label(data = survey2_topic_labels, aes(label = paste0(round(prop * 100, 1), "%")), alpha = 0.85, size = prop_text_size) +
    coord_flip(ylim = c(0.7, 7.3), expand = TRUE) +
    scale_y_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7)) +  
    labs(
      x = "Topic",
      y = "Avg. credibility") +
    #scale_fill_brewer(palette = "Greens") +
    guides(fill = F) +
    theme(
          panel.grid.major.y = element_blank(),
          panel.grid.minor.x = element_blank()
          ) 

survey2_topic
# ggsave("~/Desktop/credibility_topic_boxplots.png", survey2_topic, width = 5, height = 8)
ggsave("~/Desktop/credibility_topic_boxplots.png", survey2_topic, width = 5, height = 8)
```